Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
section 2 updates

Our study based on the Bernoulli-Beta Bayesian inference. In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, where $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$. $m$ is the order of the Dirichlet distribution.

We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice. We want to infer the probability of getting each side $\xis$. We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. The $m$ side dice change into a irregular coin with side $A$ and side $B$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.

Then we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.

>>>>

We are studying the Bayesian inference in Beta-Bernoulli systems. So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems. Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$. By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
\begin{equation*}
Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
\end{equation*}
denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

In Beta-Bernoulli systems, we take a Beta distribution as prior belief for our parameters and latent variables, $\betad(\alpha, \beta)$, where $\pi(\xi) = \betad(\xi | \alpha, \beta) = \frac{\xi^{\alpha} (1 - \xi)^{\beta}}{B(\alphas)}$, and the Bernoulli distribution as the likelihood for $Pr(\textbf{x} | \xi) = \xi^{\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}}(1 - \xi)^{n -\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}} $. %We are throwing an irregular coin with side $A$ and side $B$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.

This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$). $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i}\xi_i^{\sum\limits_{\mathrm{x_i} = x_i} \mathrm{x_i}}$.

% We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice. We want to infer the probability of getting each side $\xis$. We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.

% In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. The $m$ side dice change into a irregular coin with side $A$ and side $B$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.

The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.  we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
